Performance of Rookie Can Predict Price of Their Rookie Prizm Silver Cards

### 2024-04-21 paper/paper.qmd
saved clean data files

---
title: "Performance of Rookie Can Predict Price of Their RC based Prizm Cards"
subtitle: "My subtitle if needed"
author: 
  - Harrison Huang
thanks: "Code and data are available at: https://github.com/lemonface88/NBA"
date: today 
date-format: long
abstract: "Collecting and investing in cards has been relevant for a while now. There are complex factors that contribute to the price fluxation of these cards. This analysis will use player statistics to create a model to try to grasp possible future price trends of the card. A xxx model was used in this analysis. The results indicated that xxx is a strong indicator of the price fluctuation of potential future prices of the rookie card."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Performance of Rookie Can Predict Price of Their Rookie Prizm Silver Cards"
subtitle: "My subtitle if needed"
author: 
  - Harrison Huang
thanks: "Code and data are available at: https://github.com/lemonface88/NBA"
date: today 
date-format: long
abstract: "Collecting and investing in cards has been relevant for a while now. There are complex factors that contribute to the price fluxation of these cards. This analysis will use player statistics to create a model to try to grasp possible future price trends of the card. A xxx model was used in this analysis. The results indicated that xxx is a strong indicator of the price fluctuation of potential future prices of the rookie card."
format: pdf
number-sections: true
bibliography: references.bib
---
